\setstretch{1.3}  % Reset the line-spacing to 1.3 for body text (if it has changed)

% The Acknowledgements page, for thanking everyone
\acknowledgements{
%\addtocontents{toc}{\vspace{1em}}  % Add a gap in the Contents, for aesthetics
I take this opportunity to express my sincere gratitude and heartily thanks to my supervisor (Supervisor Name), (Department Name), National Institute of Technology Silchar for his continuous inspiration and valuable guidance at every stage of my research work. I would like to thank my Doctoral Committee Chairman and other members for their continuous evaluation and valuable constructive suggestions during this work. I would like to also thank all the faculty members of the (Your department name) of National Institute of Technology Silchar, for their administrative support during various phases of this work.

I would like to thank (your wife/father/mother/son/daughter/gf/bf) for always supporting and encouraging me during these days. I would like to thank my daughter (your wife/father/mother/son/daughter/gf/bf) who is a continuous source of inspiration for me. I would also like to thank my parents whose continuous support helped me to devote more time towards my research. 

I further, would like to thank my (some student/faculty name) for assisting me in the laboratory work. I would also like to extend my sincere thanks to my (special faculty/person name) NIT Silchar, for their valuable suggestions and discussion during my research work.

\vspace{1cm}
\begin{flushleft}
{Your Name}
\end{flushleft}
}
\clearpage  % End of the Acknowledgements
%% ----------------------------------------------------------------
\thispagestyle{empty}
\begin{center}
\vspace*{\stretch{1}}
\small{\MakeUppercase{}}%\\
%\small{\MakeUppercase{All rights reserved}}
\vspace*{\stretch{1}}
\end{center}
\clearpage
\newpage 